---
title: "Alcohol vs Seat choice"
author: "Wailana Reyes"
date: "Fall 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

I noticed that the number of people sitting in the middle is the highest (89) between the number of people sitting in the front (40) and the back (36). However, the standard deviation of the people sitting in the back is the highest (12.580471) compared to the front (3.806013) and the middle (6.225381).

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

When looking at the P-value which was about 0.000116 I noticed that it is really small telling me that there is a big statistical difference between the values.

```{r}
plot(TukeyHSD(model1))
```

Looking at the 95% confidence level. I saw the confidence intervals of the Front-Back, Middle-Back, and Middle-Front, with 0 indicating if the lines are significantly different or not. When I observed the results, I noticed that the Front-Back and Middle-Back are significantly different since 0 dooesnt go through their confidence intervals. However, for the Middle-Front seats, 0 does go through the confidence interval, indicating that there is no significant difference between them. 

## Conclusions

What I learned in this lesson is looking at numerical categorical data, but the difference this time is that there are more different categories, so I used my helper file and went down to One Way Annova to help me solve this assignment. It is more complicated than the last numerical categorical data I did, but was manageable. One way Anova provided me with numerical and inferential results I needed was by giving me the numerical results that showed people sitting in the front, middle, and back lines. I was able to see the amount of people per row, with the middle having the highest amount which was 89. I was also able to get the standard deviation values of each line and got that the back line had the highest standard deviation with 12.58041. The inferential results provided me with the P- value and it was really small, which told be that the results are significantly different, and so I went ahead and plotted a 95% confidence level chart to be able to dive more into the results. I noticed that the  I noticed that the Front-Back and Middle-Back are significantly different since 0 dooesnt go through their confidence intervals. However, for the Middle-Front seats, 0 does go through the confidence interval, indicating that there is no significant difference between them. 
